Results (Barcelona)

### 2022-02-11 docs/06_results.Rmd
Relocate files

---
title: "Results"
output: github_document
always_allow_html: true
date: "`r paste0('Updated: ', format(Sys.Date(), '%d/%m/%Y'))`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "80%",
	results = "asis",
	dpi = 300,
	dev.args = list(png = list(type = "cairo"))
)
options(
	knitr.kable.NA = '-',
	knitr.duplicate.label = "allow",
	ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
	ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
)

@@

# load objects
tar_load_globals()
tar_load(participants)
tar_load(attrition)
tar_load(vocabulary)
tar_load(gaze)
tar_load(model_fits)

@@

#### Fixed effects

```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
draws <- gather_draws(model_fits$fit, `b_.*`, `sigma`, regex = TRUE)

draws %>% 
	mean_qi(.width = c(0.95, 0.50)) %>% 
	pivot_wider(names_from = .width, values_from = c(.value, .lower, .upper)) %>% 
	clean_names() %>% 
	select(-c(point, interval, value_0_5)) %>% 
	gt(rowname_col = "variable") %>% 
	fmt_number(2:6) %>% 
	cols_merge(c("lower_0_95", "upper_0_95"), pattern = "[{1}, {2}]") %>% 
	cols_merge(c("lower_0_5", "upper_0_5"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		variable = md("**Predictor**"),
		value_0_95 = md("**Mean**"),
		lower_0_95 = md("**95% CrI**"),
		lower_0_5 = md("**50% CrI**")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#b9fac4")
		),
		locations = cells_body(
			columns = lower_0_95,
			rows = lower_0_95 > 0
		)
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#b9fac4")
		),
		locations = cells_body(
			columns = lower_0_5,
			rows = lower_0_5 > 0
		)
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#fabfb9")
		),
		locations = cells_body(
			columns = lower_0_95,
			rows = upper_0_95 < 0
		)
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#fabfb9")
		),
		locations = cells_body(
			columns = lower_0_5,
			rows = upper_0_5 < 0
		)
	) %>% 
	as_raw_html()
```

```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE}

draws %>% 
	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
	mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4)) %>% 
	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95))))) +
	geom_vline(xintercept = 0, colour = "black") +
	stat_halfeye(point_color = "black", interval_color = "black") +
	labs(x = "Value", y = "Variable", fill = "CrI") +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	theme(
		axis.title = element_blank(),
		legend.position = "top"
	)

@@

#### Random effects

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

vcov(model_fits$fit) %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
	filter(!grepl("time_bin", term1), !grepl("time_bin", term2)) %>% 
	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
	geom_tile() +
	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
	scale_fill_distiller(limits = c(-1, 1)) +
	coord_equal() +
	theme(
		legend.position = "top",
		legend.text = element_text(size = 8),
		axis.title = element_blank(),
		axis.text.y = element_text(hjust = 1, size = 7),
		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
	)

@@

#### Marginal means {.tabset }

##### Marginal to time course

@@

m <- emmeans(model_fits$fit, ~trial_type:lp, by = "age_group", epred = TRUE) %>% 
	as_tibble() %>% 
	clean_names() %>% 
	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x < 0, 0, x)) %>% 
	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x > 1, 1, x))

ggplot(m, aes(age_group, emmean, ymin = lower_hpd, ymax = upper_hpd, colour = trial_type)) +
	facet_wrap(~lp, ncol = 1) +
	# geom_line(aes(group = trial_type), size = 1, position = position_dodge(width = 0.25)) +
	geom_errorbar(size = 1, width = 0, position = position_dodge(width = 0.25)) +
	geom_point(size = 4, position = position_dodge(width = 0.25)) +
	labs(x = "Age (months))", y = "P(target)", colour = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent)  +
	theme(
		legend.title = element_blank(),
		legend.position = "top"
	)

@@

##### Time course

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(valid_participant) %>% 
	count(lp, age_group)

n <- expand_grid(
	lp = c("Monolingual", "Bilingual"),
	age_group = paste(c(21, 25, 30), "months"),
	trial_type = unique(gaze$trial_type),
	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.5)
)

m <- epred_draws(object = model_fits$fit, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(.value = logit_to_prob(.epred))

>>>>

---
title: "Results (Barcelona)"
output: github_document
always_allow_html: true
date: "`r paste0('Updated: ', format(Sys.Date(), '%d/%m/%Y'))`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "80%",
	results = "asis",
	dpi = 300,
	dev.args = list(png = list(type = "cairo"))
)
options(
	knitr.kable.NA = '-',
	knitr.duplicate.label = "allow",
	ggplot2.discrete.fill = ggsci::pal_futurama()(7),
	ggplot2.discrete.colour = ggsci::pal_futurama()(7)
)

@@

# load objects
tar_load_globals()
tar_load_all()

@@

# Model comparison

```{r model-comparison, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

model_comparison <- waics_l1 %>% 
	map("estimates") %>% 
	map(function(x) rownames_to_column(as.data.frame(x), "variable")) %>% 
	bind_rows(.id = "model") %>%
	clean_names() %>% 
	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
	mutate(
		model = c(
			"Intercept",
			"... + Trial type",
			"... + Group \u00d7Trial type\u00d7Group",
			"... + Vocab. + Trial type\u00d7Vocab. + Group\u00d7Vocab.",
			"... + Trial type\u00d7Vocab. + Group\u00d7Vocab. + Trial type\u00d7Group\u00d7Vocab."
		)
	) %>% 
	gt() %>% 
	fmt_number(-model) %>% 
	tab_spanner("WAIC", matches("waic")) %>% 
	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
	cols_label(
		model = "Model",
		estimate_elpd_waic = "Estimate",
		estimate_waic = "Estimate",
		estimate_p_waic = "Estimate",
		se_elpd_waic = md("*SE*"),
		se_waic = md("*SE*"),
		se_p_waic = md("*SE*"),
	) %>% 
	cols_align("right", "model") %>% 
	tab_style(
		cell_text(weight = "bold"),
		cells_column_spanners()
	) %>% 
	tab_style(
		cell_text(style = "italic"),
		cells_column_labels()
	)

gtsave(model_comparison, here("img", "model_comparison.png"))

as_raw_html(model_comparison)

@@

# Model with total vocabulary

## Fixed effects

```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
str_repl <- c(

	# 3-way interactions
	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" = 
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",

	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",

	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (total)",
	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (total)",

	# 2-way interactions
	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_total_center" = 
		"Trial type (C vs. NC) \u00d7 Vocab (total)",

	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
		"Trial type (U vs. C+NC) \u00d7 Group",
	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_total_center" =
		"Trial type (C vs. NC) \u00d7 Vocab (total)",

	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" =
		"Trial type (U vs. C+NC) \u00d7 Group",  
	"b_time_bin_center:lpLPMonvs.Bil:vocab_size_total_center" =
		"Group \u00d7 Vocab (total)",

	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_total_center" = 
		"Trial type (C vs. NC) \u00d7 Vocab (total)",

	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
		"Trial type (U vs. C+NC) \u00d7 Group",
	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil" =
		"Trial type (C vs. NC) \u00d7 Group",

	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:vocab_size_total_center" = 
		"Trial type (C vs. NC) \u00d7 Vocab (total)",

	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
		"Trial type (U vs. C+NC) \u00d7 Group",  
	"b_Itime_bin_centerE2:lpLPMonvs.Bil:vocab_size_total_center" = 
		"Group \u00d7 Vocab (total)",

	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_total_center" = 
		"Trial type (C vs. NC) \u00d7 Vocab (total)",

	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
		"Trial type (U vs. C+NC) \u00d7 Group",
	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab (total)",
	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:vocab_size_total_center" = 
		"Trial type (C vs. NC) \u00d7 Vocab (total)",

	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
		"Trial type (U vs. C+NC) \u00d7 Group",  
	"b_Itime_bin_centerE3:lpLPMonvs.Bil:vocab_size_total_center" = 
		"Group \u00d7 Vocab (total)",

	# main effects (linear)
	"b_time_bin_center:trial_typePrimeUvs.CPNC" =
		"Trial type (U vs. C+NC)",
	"b_time_bin_center:trial_typePrimeNCvs.C" = 
		"Trial type (C vs. NC)",
	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC" = 
		"Trial type (U vs. C+NC)",
	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C" = 
		"Trial type (C vs. NC)",
	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" = 
		"Trial type (U vs. C+NC)",
	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" = 
		"Trial type (C vs. NC)",

	"b_time_bin_center:lpLPMonvs.Bil" = 
		"Group (Mon. vs. Bil.)",
	"b_Itime_bin_centerE2:lpLPMonvs.Bil" = 
		"Group (Mon. vs. Bil.)",
	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
		"Group (Mon. vs. Bil.)",

	"b_time_bin_center:vocab_size_total_center" = 
		"Vocab. (total, +1 SD)",
	"b_Itime_bin_centerE2:vocab_size_total_center" = 
		"Vocab. (total, +1 SD)",
	"b_Itime_bin_centerE3:vocab_size_total_center" = 
		"Vocab. (total, +1 SD)",

	# 3-way interaction linear effects
	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_total_center" =
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab. (total, +1 SD)",
	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_total_center" =
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab. (total, +1 SD)",

	# 2-way interaction linear effects
	"b_trial_typePrimeUvs.CPNC:lpLPMonvs.Bil" = 
		"Trial type (U vs. C+NC) \u00d7 Group",
	"b_trial_typePrimeNCvs.C:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

	"b_trial_typePrimeUvs.CPNC:vocab_size_total_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab. (total, +1 SD)",
	"b_trial_typePrimeNCvs.C:vocab_size_total_center" = 
		"Trial type (C vs. NC) \u00d7 Vocab. (total, +1 SD)",

	"b_lpLPMonvs.Bil:vocab_size_total_center" =
		"Group \u00d7 Vocab. (total, +1 SD)",

	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC" =
		"Trial type (U vs. C+NC)",
	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C" =
		"Trial type (C vs. NC)",

	"b_Itime_bin_centerE3:lpLPMonvs.Bil" = 
		"Group (Mon. vs. Bil.)",

	# main linear effects
	"b_Intercept" = "Intercept",
	"b_Itime_bin_centerE2" = "Time bin 2",
	"b_Itime_bin_centerE3" = "Time bin 3",
	"b_time_bin_center" = "Time bin",
	"b_vocab_size_total_center" = "Vocab. (total, +1 SD)",

	"b_trial_typePrimeUvs.CPNC" = "Trial type (U vs. C+NC)",
	"b_trial_typePrimeNCvs.C" = "Trial type (C vs. NC)",
	"b_lpLPMonvs.Bil" = "Group (Mon. vs. Bil.)",

	# sigma
	"sigma" = "Sigma"
)

draws <- gather_draws(fit_total_4, `b_.*`, `sigma`, regex = TRUE) %>% 
	mutate(
		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
		.variable_name = str_replace_all(.variable, str_repl),
		type = case_when(
			str_detect(.variable, "E2") ~ "Quadratic time",
			str_detect(.variable, "E3") ~ "Cubic time",
			str_detect(.variable, "time_bin") ~ "Linear time",
			str_detect(.variable, "sigma") ~ "Error",
			TRUE ~ "Main effects"
		) %>% 
			factor(levels = c("Main effects", "Linear time", "Quadratic time", "Cubic time", "Error"), ordered = TRUE)
	)

draws %>% 
	group_by(.variable, .variable_name, type) %>% 
	mean_qi() %>% 
	select(type, .variable_name, .value, .lower, .upper) %>% 
	gt(rowname_col = ".variable", groupname_col = "type")  %>% 
	fmt_percent(3) %>%
	fmt_number(4:5, scale_by = 100) %>% 
	cols_merge(c(".lower", ".upper"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		.variable_name = md("**Predictor**"),
		.value = md("**Mean**"),
		.lower = md("**95% CrI**")
	) %>% 
	tab_style(
		style = list(
			cell_text(weight = "bold", style = "italic")
		),
		locations = list(
			cells_row_groups()
		)
	) %>% 
	tab_style(
		style = list(
			cell_text(weight = "bold")
		),
		locations = list(
			cells_column_labels()
		)
	) %>% 
	as_raw_html()
```

```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}

draws_intercept <- draws %>% 
	filter(str_detect(.variable, "Intercept")) %>% 
	ggplot(aes(.value, .variable_name)) +
	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(0.95, 0.8, 0.5), labels = percent_format()))),
		size = 0.5,
		color = "#FF6F00FF",
		fill = "#FF6F00FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		title = "Intercept",
		alpha = "CrI"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		axis.title.y = element_blank()
	)

draws_predictors <- draws %>% 
	filter(str_detect(.variable, "Intercept|sigma|sd|time_bin", negate = TRUE)) %>% 
	ggplot(aes(.value, .variable_name)) +
	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5, 
		color = "#C71000FF", 
		fill = "#C71000FF") +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Main effects"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(-0.2, 0.2)) +
	theme(
		axis.title.y = element_blank()
	)

draws_time <- draws %>%
	filter(str_detect(.variable, "time_bin")) %>% 
	ggplot(aes(.value, .variable_name)) +
	facet_wrap(~type, scales = "free_x") +
	geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
	# stat_slab(
	# 	aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
	# 	size = 0.5, 
	# 	color = "#008EA0FF", 
	# 	fill = "#008EA0FF"
	# ) +
	stat_pointinterval(
		color = "#008EA0FF",
		fill = "#008EA0FF",
		point_size = 1.5
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Polynomial effects"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent) +
	theme(
		axis.title.y = element_blank()
	)

draws_sigma <- draws %>% 
	filter(str_detect(.variable, "sigma")) %>% 
	ggplot(aes(.value, .variable_name)) +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		size = 0.5, 
		color = "#8A4198FF", 
		fill = "#8A4198FF"
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		alpha = "CrI",
		fill = "CrI", 
		title = "Error"
	) +
	guides(fill = "none", color = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(0.92, 0.97)) +
	theme(
		axis.title.y = element_blank()
	)

((draws_intercept / draws_sigma / guide_area()) | draws_predictors) /
	draws_time + 
	plot_layout(heights = c(0.5, 0.5)) &
	guides(fill = "none", color = "none") &
	theme(
		panel.background = element_rect(fill = NA, colour = "grey"),
		axis.text.y = element_text(size = 7),
		axis.text.x = element_text(size = 7),
		axis.title = element_blank(),
		legend.position = c(1, 1.2),
		legend.direction = "horizontal",
		legend.justification = "right",
		legend.key.size = unit(0.35, "cm"),
		legend.text = element_text(size = 7),
		legend.title = element_text(size = 7),
		panel.grid.major.y = element_blank()
	)

@@

## Random effects

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, fig.height=4}

corr_mat <- VarCorr(fit_total_4, summary = TRUE)$participant$cor 
corr_names <- rownames(VarCorr(fit_total_4, summary = TRUE)$participant$cor)

corr_mat <- corr_mat %>% 
	as_tibble() %>% 
	select(matches("Estimate")) %>% 
	rename_all(str_remove, "Estimate.") %>% 
	mutate(term1 = corr_names)

corr_mat[lower.tri(corr_mat)] <- NA

corr_data <- corr_mat %>% 
	as.data.frame() %>% 
	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
	drop_na(.value)

post_cors_participant <- corr_data %>% 
	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
	mutate(
		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
	) %>% 
	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
	geom_tile(na.rm = TRUE) +
	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
	labs(
		x = "Term 1", 
		y = "Term 2", 
		fill = "Posterior\ncorrelation",
		title = "By participant"
	) +
	scale_fill_gradient2(
		low = "#04bf78", mid = "white", high = "#FFC20A", 
		na.value = "white", limits = c(-0.4, 0.4)
	) +
	scale_x_discrete() +
	coord_equal() +
	theme(
		axis.text.y = element_text(size = 6, vjust = 1, hjust = 1)
	)

# correlations by item
corr_mat <- VarCorr(fit_total_4, summary = TRUE)$target$cor 
corr_names <- rownames(VarCorr(fit_total_4, summary = TRUE)$target$cor)

corr_mat <- corr_mat %>% 
	as_tibble() %>% 
	select(matches("Estimate")) %>% 
	rename_all(str_remove, "Estimate.") %>% 
	mutate(term1 = corr_names)

corr_mat[lower.tri(corr_mat)] <- NA

corr_data <- corr_mat %>% 
	as.data.frame() %>% 
	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
	drop_na(.value)

post_cors_item <- corr_data %>% 
	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
	mutate(
		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
	) %>% 
	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
	geom_tile(na.rm = TRUE) +
	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
	labs(
		x = "Term 1", y = "Term 2", fill = "Posterior\ncorrelation",
		title = "By item"
	) +
	scale_fill_gradient2(
		low = "#04bf78", mid = "white", high = "#FFC20A", 
		na.value = "white", limits = c(-0.4, 0.4)
	) +
	scale_x_discrete() +
	coord_equal()  +
	theme(
		axis.text.y = element_blank()
	)

(post_cors_participant | post_cors_item) &
	plot_layout(guides = "collect") &
	theme(
		panel.grid = element_blank(),
		legend.position = "top",
		legend.direction = "horizontal",
		legend.key.height = unit(0.1, "cm"),
		legend.key.width = unit(0.3, "cm"),
		legend.justification = c(1, 1),
		legend.title = element_blank(),
		legend.text = element_text(size = 5),
		axis.title.x = element_blank(),
		axis.title.y = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1)
	)

## Marginal means

### Prior predictions (before seeing the data)

```{r gaze_time_prior, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(valid_participant) %>% 
	count(lp, vocab_size_total_center)

n <- expand_grid(
	lp = c("Monolingual", "Bilingual"),
	vocab_size_l1_center = c(-1, 1),
	trial_type = unique(gaze$trial_type),
	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
)

m <- epred_draws(fit_l1_prior, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(
		.value = logit_to_prob(.epred),
		vocab_size_l1_center = ifelse(
			vocab_size_l1_center==-1, 
			"Low vocabulary size (-1 SD)",
			"High vocabulary size (+1 SD)"
		)
	)

ggplot(m, aes(time_bin_center, .value)) +
	facet_grid(fct_rev(lp)~vocab_size_l1_center) +
	geom_hline(yintercept = 0.5, colour = "black") +
	geom_line(
		aes(group = interaction(vocab_size_l1_center, trial_type, lp, .draw),
			colour = trial_type),
		alpha = 0.5, size = 0.65
	) +

	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
	scale_color_futurama() +
	scale_x_continuous(
		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
		labels = 1:20
	) +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme_minimal() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 7),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(fill = "white", colour = NA),
		plot.background = element_rect(fill = "white", colour = NA)
	)

### Posterior predictions (after seeing the data)

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(valid_participant) %>% 
	count(lp, vocab_size_total_center)

n <- expand_grid(
	lp = c("Monolingual", "Bilingual"),
	vocab_size_total_center = c(-1, 1),
	trial_type = unique(gaze$trial_type),
	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
)

m <- epred_draws(object = fit_total_4, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(
		.value = logit_to_prob(.epred),
		vocab_size_total_center = ifelse(
			vocab_size_total_center==-1, 
			"Low vocabulary size (-1 SD)",
			"High vocabulary size (+1 SD)"
		)
	)

ggplot(m, aes(time_bin_center, .value)) +
	facet_grid(fct_rev(lp)~vocab_size_total_center) +
	geom_hline(yintercept = 0.5, colour = "black") +
	geom_line(
		aes(group = interaction(vocab_size_total_center, trial_type, lp, .draw),
			colour = trial_type),
		alpha = 0.5, size = 0.65
	) +
	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
	scale_color_futurama() +
	scale_x_continuous(
		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
		labels = 1:20
	) +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme_minimal() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 7),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(fill = "white", colour = NA),
		plot.background = element_rect(fill = "white", colour = NA)
	)

## Marginal means {.tabset }

@@

m <- emmeans(fit_total_4, ~trial_type | lp, epred = TRUE)

m_draws <- gather_emmeans_draws(m) %>% 
	as_tibble() %>% 
	mutate_at(vars(.value), function(x) ifelse(x < 0, 0, x)) %>% 
	mutate_at(vars(.value), function(x) ifelse(x > 1, 1, x))

ggplot(m_draws, aes(.value, trial_type, fill = trial_type)) +
	facet_wrap(~lp) +
	stat_slab(
		aes(alpha = stat(cut_cdf_qi(cdf, .width = c(.95, .8, .5), labels = percent_format()))),
		position = position_nudge(y = 0.05),
		color = "white"
	) +
	stat_pointinterval(
		color = "black"
	) +
	labs(
		x = "Expected posterior mean PTLT", y = "Trial type",
		colour = "Trial type", fill = "Trial type",
		alpha = "CrI"
	) +
	guides(color = "none", fill = "none") +
	scale_alpha_discrete(range = c(0.8, 0.2), na.translate = FALSE) +
	scale_x_continuous(limits = c(0.5, 1), labels = percent)  +
	theme(
		axis.title.y = element_blank(),
		legend.position = "right",
		panel.grid.major.y = element_blank(),
		panel.grid.minor.y = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(fill = NA, colour = "grey")
	)

@@

# Model with L1 vocabulary

## Fixed effects

```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
str_repl <- c(

	# 3-way interactions
	"b_time_bin_center:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (L1)",
	"b_time_bin_center:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" = 
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",

	"b_Itime_bin_centerE2:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (L1)",
	"b_Itime_bin_centerE2:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",

	"b_Itime_bin_centerE3:trial_typePrimeNCvs.C:lpLPMonvs.Bil:vocab_size_l1_center" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Vocab (L1)",
	"b_Itime_bin_centerE3:trial_typePrimeUvs.CPNC:lpLPMonvs.Bil:vocab_size_l1_center" =
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Vocab (L1)",

	# 2-way interactions
	"b_time_bin_center:trial_typePrimeUvs.CPNC:vocab_size_l1_center" = 
		"Trial type (U vs. C+NC) \u00d7 Vocab (L1)",
	"b_time_bin_center:trial_typePrimeNCvs.C:vocab_size_l1_center" = 
		"Trial type (C vs. NC) \u00d7 Vocab (L1)",
